---
output: html_document
editor_options: 
  chunk_output_type: inline
---
```{r eval=T, echo=FALSE}
klippy::klippy()
```


# Geometries and Aesthetics

-   [Available geometries](https://ggplot2.tidyverse.org/reference/index.html#section-layers)

-   Two steps:

    -   Step 1: What geometries do you see?

    -   Step 2: With a given geometry, what aesthetics do you observe?

------------------------------------------------------------------------

```{r , eval=T, echo=F}
teachDS::img_centering("https://i0.wp.com/cmdlinetips.com/wp-content/uploads/2019/11/scatter_plot_with_ggplot_scale_xy_log10_color.png")
```

-   Geometries?

-   Aesthetics?

------------------------------------------------------------------------

```{r , eval=T, echo=F}
teachDS::img_centering("https://belayeth.com/wp-content/uploads/2021/06/Rplot.png")
```

------------------------------------------------------------------------

```{r , eval=T, echo=F}
teachDS::img_centering("https://www.r-graph-gallery.com/img/graph/50-51-52-scatter-plot-with-ggplot2.png")
```

------------------------------------------------------------------------

```{r , eval=T, echo=F}
teachDS::img_centering("https://www.economist.com/img/b/1280/755/90/sites/default/files/images/2021/09/articles/main/20210918_woc289.png")
```

## An Example

```{r , eval=T, echo=F}
teachDS::img_centering("https://www.economist.com/img/b/600/895/90/sites/default/files/images/2021/09/articles/body/20210918_woc287.png")
```

-   Geom:\
    [`geom_point`](https://ggplot2.tidyverse.org/reference/geom_point.html):

    -   x, y：varies with observations

    -   color (線框顏色): constant

    -   stroke (線框粗細): constant

    -   fill (內部塗色): constant

    -   size (點的大小): constant

    [`geom_text`](https://ggplot2.tidyverse.org/reference/geom_text.html#aesthetics):

    -   x, y: varies with observations

    -   label: varies with observations

    -   hjust (文字水平錨點）：between 0 and 1

    -   vjust (文字垂直錨點）: between 0 and 1

```{r}
if(!require("R6")) install.packages("R6")

```

```{r}
Action = R6::R6Class("Action",
  public=list(
    change=function(data){
      # print(self$data)
      data+3
    }
  ),
  lock_objects = F)

Person = R6::R6Class("Person",
  inherit = Action,
  public = list(
    data=NULL,
    newData=NULL,
    initialize = function(data){
      print(data)
      self$data=data
      print(self)
      # invisible(self.data)
    },
    changeMyself=function(){
      print(super)
      self$newData = Action$public_methods$change(self$data)
    }
  ))

p1 = Person$new(22)
p1$data
p1$changeMyself()
p1$newData

Action$public_methods$change <- function(data) data**2

p1$data
p1$changeMyself()
p1$newData
```


```{r}
GG <- R6::R6Class(
  "GG",
  public=list(
    # fields
    data=NULL,
    initialize=function(data){
      self$data = data;
    },
    change=function(){
      self$data+4
    }
  ),
  lock_objects = F
)
plot1= GG$new(data=1)

class(GG)
typeof(GG)
print(GG)
typeof(plot1)
print(plot1)
parent.env(plot1)
```

## Environment

```{r globalenv}
person1 = list(
  name="Lisa", 
  greet=function(){"Hi, I am Lisa."})
person2 = list(
  name="Bob",
  greet=function(){"Hi, I am Bob."}
)

# created two objects in Global environment
person1
person2

person1$greet()
person2$greet()
```


Environment is a special object created via:

```{r newEnv}
# create an environment
myEnv = new.env()

# populate the environment
myEnv$person1 = list(
  name="Lisa2", 
  greet=function(){paste("Hi, I am Lisa2.")})
myEnv$person2 = list(
  name="Bob2",
  greet=function(){"Hi, I am Bob2."}
)

# Get person1/2 from R search path starting from global environment
person1$greet() 
person2$greet()  

# Get person1/2 from a specific environment
myEnv$person1$greet()
myEnv$person2$greet()
```

You can also:
```{r}
myEnv = new.env()
with(myEnv,{
  person1 = list(
    name="Lisa2", 
    greet=function(){paste("Hi, I am Lisa2.")})
  person2 = list(
    name="Bob2",
    greet=function(){"Hi, I am Bob2."}
  )
})

```

###  Mutable

```{r changeEnv1}
changePerson1 = function(){
  # search path: exec env -> global env   
  person1$name="John"
  person1$greet=function() "Hi I am John"
}
# the object called is from the global env, but the object is not modified.
changePerson1() 
person1$name
person1$greet()

```

Anything inside an environment can be changed no matter where the environment is called.

```{r}
changePerson1 = function(){
  .GlobalEnv$person1$name="John"
  .GlobalEnv$person1$greet=function() "Hi I am John"
}

changePerson1()
person1
```

### ggplot application 

  * Source data
  
  * Data cleaning
  
  * Basic plotting
  
  * fine tune

```{r}

plot = new.env()
plot$data = data.frame(
    x=c(52.5, 56, 58.5),
    y=c(48.6, 54.9, 58),
    label=c("Colombia", "Norway", "Germany")
  )
plot$graph = function(){
    require(ggplot2)
    ggplot()+
      geom_point(data=plot$data, # accessing to an object within an environment
        mapping=aes(
          x=x, y=y
        ),
        fill="blue", 
        shape=21,  
        color="black",
        stroke=1,
        size=1 )
}

plot$graph()
```

### Flexibility

Environment object is flexible to change any member. 

```{r}
plot$graph <- function(){
  require(ggplot2)
  ggplot()+
    geom_point(
      data=plot$data,
      mapping=aes(
        x=x, y=y
      ),
      fill="blue", #input$fill_point
      shape=21, # default point is a circle without border, you need another type of point
      color="black", #input$color_point
      stroke=1, #input$stroke_point
      size=1 #input$size_point
    )+
    geom_text(
      data=plot$data,
      mapping=aes(
        x=x, y=y, label=label
      ),
      hjust = 1, #input$hjust_text
      size = 1 #input$size_text
    )
}


plot$graph()
```

### Plot constructor

```{r}
Plot = function(.data=NULL, .graph=NULL){
  self = new.env()
  self$data = .data
  self$graph = .graph
  return(self)
}
```


```{r}
plot = Plot()
plot$data = data.frame(
    x=c(52.5, 56, 58.5),
    y=c(48.6, 54.9, 58),
    label=c("Colombia", "Norway", "Germany")
  )
plot$graph = function(){
    require(ggplot2)
    ggplot()+
      geom_point(data=plot$data, # accessing to an object within an environment using self$ or plot$
        mapping=aes(
          x=x, y=y
        ),
        fill="blue", 
        shape=21,  
        color="black",
        stroke=1,
        size=1 )
}
plot$graph()
```


```{r}
# change data
plot$data = data.frame(
    x=c(52.5, 46, 58.5),
    y=c(48.6, 54.9, 78),
    label=c("Colombia", "Norway", "Germany")
  )
plot$graph()
```

```{r}
# change graph
plot$graph = function(){
  require(ggplot2)
  ggplot()+
    geom_point(
      data=plot$data,
      mapping=aes(
        x=x, y=y
      ),
      fill="blue", #input$fill_point
      shape=21, # default point is a circle without border, you need another type of point
      color="black", #input$color_point
      stroke=1, #input$stroke_point
      size=1 #input$size_point
    )+
    geom_text(
      data=plot$data,
      mapping=aes(
        x=x, y=y, label=label
      ),
      hjust = 1, #input$hjust_text
      size = 1 #input$size_text
    )
}
plot$graph()
```


### econDV2::ggdash

  * At every aesthetic element to be adjusted, attach `#input${aesthetic_name}` at the end of the line as:

  
```{r}
  ggplot()+
    geom_point(
      data=plot$data,
      mapping=aes(
        x=x, y=y
      ),
      fill="blue", #input$fill_point
      shape=21, # default point is a circle without border, you need another type of point
      color="black", #input$color_point
      stroke=1, #input$stroke_point
      size=1 #input$size_point
    )+
    geom_text(
      data=Plot$data,
      mapping=aes(
        x=x, y=y, label=label
      ),
      hjust = 1, #input$hjust_text
      size = 1 #input$size_text
    )
```

  
  * Select only the `ggplot()` part of code.
  
  * Run `gg$dash()`





### ggdash more

  * ggdash can control any input within a programming block

```{r}
myplot2 <- {
  myshape = 21 #input$shape_point
  ggplot() +
    geom_point(
      data = data4plot$point$data,
      mapping = aes(
        x = x, y = y
      ),
      fill = "#2fc1d3",
      shape = myshape,
      color = "black",
      stroke = 1,
      size = 12
    ) +
    geom_text(
      data = data4plot$text$data,
      mapping = aes(
        x = x + 
          0, #input$x_text
        y = y, label = label
      ),
      hjust = 0,
      size = 12
    )
}
myplot2
```

## Inheritance


### Data

  * Common data source can be put in `ggplot()`:
  
    * **ALL** geoms will use the same data to find aes() mapping,
    
    * **UNLESS** the geom has its own data supplied.

```{r}
data = data4plot$text$data

myplot <- {
  ggplot(data = data,
) +
    geom_point(
      mapping = aes(
        x = x, y = y
      ),
      fill = "#2fc1d3",
      shape = 21,
      color = "black",
      stroke = 1,
      size = 12
    ) +
    geom_text(
      # data = data4plot$text$data,
      mapping = aes(
        x = x, y = y, label = label
      ),
      hjust = 0,
      size = 12
    )
}

```

### Aesthetics

```{r}
myplot <- {
  ggplot(
    data = data,
    mapping = aes(x=x, y=y)
) +
    geom_point(
      fill = "#2fc1d3",
      shape = 21,
      color = "black",
      stroke = 1,
      size = 12
    ) +
    geom_text(
      mapping = aes(
        label = label
      ),
      hjust = 0,
      size = 12
    )
}
myplot
```

```{r}
plot_hightlightCountries <- function(data) {
  myplot <- {
    ggplot(data = data,
  ) +
      geom_point(
        mapping = aes(
          x = x, y = y
        ),
        fill = "#2fc1d3",
        shape = 21,
        color = "black",
        stroke = 1,
        size = 12
      ) +
      geom_text(
        # data = data4plot$text$data,
        mapping = aes(
          x = x, y = y, label = label
        ),
        hjust = 0,
        size = 12
      )
  }
  myplot
}
```

### Stop data inheritance

  * When a **geom has its own data supplied**, data inheritance stops.

```{r}
nonhighlightedCountries <-
  data.frame(
    x=c(48, 52, 53),
    y=c(48, 53, 54)
  )
highlightedCountries <- data4plot$text$data

plot_allCountries <- 
{
  plot_hightlightCountries(highlightedCountries) +
    geom_point(
      data = nonhighlightedCountries,
      aes(
        x=x,
        y=y
      ),
      size = 12,
      color= "#a4dce6"
    )
}

plot_allCountries
```

```{r}
plot_allCountries <- function(highlightedCountries, nonhighlightedCountries) {
  plot_hightlightCountries(highlightedCountries) +
    geom_point(
      data = nonhighlightedCountries,
      aes(
        x=x,
        y=y
      ),
      size = 12,
      color= "#a4dce6"
    )
}

```

### Finish panel

```{r}
plot_obsessionWithBorders <- {
  plot_allCountries(
    hightlightedCountries = highlightedCountries,
    unhighlightedCountries = unhighlightedCountries
  )+
  geom_abline(
    aes(
      slope=1,
      intercept=0
    ),
    color = "#549ab6",
    linetype = 2,
    size=2
  )
}
plot_obsessionWithBorders
```
```{r}
plot_obsessionWithBorders +
  geom_abline(
    aes(
      slope=1,
      intercept=0
    ),
    color = "#549ab6",
    linetype = 2,
    size=2
  )
```

```{r}
hightlightXYequal <- function(plot_obsessionWithBorders) {
  plot_obsessionWithBorders +
    geom_abline(
      aes(
        slope=1,
        intercept=0
      ),
      color = "#549ab6",
      linetype = 2,
      size=2
    )
}
```

## Graph export

The easiest way to export the graph as you see on `gg$dash()` is to right click the image on the shiny dashboard and choose **save image as** to export the image. 

